### 2020-12-01 paper/localpsf.tex
editing intro

Let $\Omega \subset \mathbb{R}^d$ be a bounded domain, and let $\mathcal{A}:L^2(\Omega)\rightarrow L^2(\Omega)'$ be an integral operator of the form
\begin{equation}
\label{eq:kernel_representation}
(\mathcal{A}u)(v) := \int_\Omega \int_\Omega v(y) A(y,x) u(x) dx dy,
\end{equation}
with integral kernel $A:\Omega \times \Omega \rightarrow \mathbb{R}$. We focus on operators of this form which have the following properties:
\begin{description}
\item[Matrix-free:] One cannot easily access kernel entries $A(y,x)$. Access to $\mathcal{A}$ is available through application of $\mathcal{A}$ and $\mathcal{A}^T$ to arbitrary vectors, $u \mapsto\mathcal{A}u$ and $v \mapsto\mathcal{A}^Tv$. 
\item[Non-negative:] $A(y,x) \ge 0$ for all $(y,x) \in \Omega \times \Omega$.
\item[Local support:] $A(y, x)$ is supported near $y=x$.
\item[Local translation invariance:] $A(y+h, x+h) \approx A(y,x)$
if $h$ is not too large.
\end{description}
Access to $\mathcal{A}$ is available through application of $\mathcal{A}$ and $\mathcal{A}^T$ to arbitrary vectors, $u \mapsto\mathcal{A}u$ and $v \mapsto\mathcal{A}^Tv$.
Integral kernel representation \eqref{eq:kernel_representation} is assumed to exist,
%e.g., by the Schwarz kernel theorem,
but o
One cannot easily access entries $A(y,x)$ of the kernel.

% is non-negative in the sense that  $A(y,x) \ge 0$ for all $(y,x) \in \Omega \times \Omega$. 
%Let $\mathcal{A}:L^2(\Omega)\rightarrow L^2(\Omega)'$ be the corresponding linear operator generated by currying. That is, for each $u\in L^2(\Omega)$, the linear functional $\mathcal{A}u:L^2(\Omega)\rightarrow \mathbb{R}$ is 
%We approximate the operator $\mathcal{A}:L^2(\Omega)\rightarrow L^2(\Omega)'$ defined by
%\begin{equation*}
%	(\mathcal{A}u)(v) := a(v,u).
%\end{equation*}
%We seek to approximate operators $\mathcal{A}$ in the ``matrix free'' setting, in which access to $\mathcal{A}$ is available through application of $\mathcal{A}$ and $\mathcal{A}^T$ to arbitrary vectors, $u \mapsto\mathcal{A}u$ and $v \mapsto\mathcal{A}^Tv$. Here ($\mathcal{A}^Tv)(u) := (\mathcal{A}u)(v)$. 
Integral kernel representation \eqref{eq:kernel_representation} is assumed to exist,
%e.g., by the Schwarz kernel theorem,
but one cannot easily access entries $A(y,x)$ of the kernel. We assume that the impulse response of $\mathcal{A}$ is locally supported in the sense that the function 
$y \mapsto A(y, x)$ is supported in a region near $y=x$, and we assume that $\mathcal{A}$ is locally translation invariant in the sense that
\begin{equation*}
A(y+h, x+h) \approx A(y,x),
\end{equation*}
so long as $h$ is not too large.

>>>>

Let $\Omega \subset \mathbb{R}^d$ be a bounded domain, and let $\mathcal{A}:L^2(\Omega)\rightarrow L^2(\Omega)'$ be an integral operator of the form
\begin{equation}
\label{eq:kernel_representation}
(\mathcal{A}u)(v) := \int_\Omega \int_\Omega v(y) A(y,x) u(x) dx dy,
\end{equation}
with integral kernel $A:\Omega \times \Omega \rightarrow \mathbb{R}$. We focus on operators of this form which have the following properties:
\begin{description}
\item[Matrix-free:] One cannot easily access kernel entries $A(y,x)$. Access to $\mathcal{A}$ is available through application of $\mathcal{A}$ and $\mathcal{A}^T$ to arbitrary vectors, $u \mapsto\mathcal{A}u$ and $v \mapsto\mathcal{A}^Tv$. 
\item[Non-negative:] $A(y,x) \ge 0$ for all $(y,x) \in \Omega \times \Omega$.
\item[Local support:] $A(y, x)$ is supported near $y=x$.
\item[Local translation invariance:] $A(y+h, x+h) \approx A(y,x)$
if $h$ is not too large.
\end{description}
If $\mathcal{A}$ were translation invariant---i.e., if the exact equality $A(y+h, x+h) = A(y,x)$ held for arbitrary $x$, $y$, $h$---then it is straightforward to show that $\mathcal{A}$ would take the form of a convolution operator $\left(\mathcal{A}u\right)(v) = \left\langle v, \varphi_p \ast u\right\rangle_{L^2(\Omega)}$. The convolution kernel,
\begin{equation*}
	\varphi_x(y) := A(y+x,x)
\end{equation*}
is the result of applying $\mathcal{A}$ to a point source at some fixed point $x$, then translating the resulting impulse response function re-center it at zero instead of $x$. Locally translation invariant operators therefore act like convolution operators locally, but the convolution kernel, $\varphi_x$, varies as $x$ changes.

%Access to $\mathcal{A}$ is available through application of $\mathcal{A}$ and $\mathcal{A}^T$ to arbitrary vectors, $u \mapsto\mathcal{A}u$ and $v \mapsto\mathcal{A}^Tv$.
%Integral kernel representation \eqref{eq:kernel_representation} is assumed to exist,
%e.g., by the Schwarz kernel theorem,
%but o
%One cannot easily access entries $A(y,x)$ of the kernel.

% is non-negative in the sense that  $A(y,x) \ge 0$ for all $(y,x) \in \Omega \times \Omega$. 
%Let $\mathcal{A}:L^2(\Omega)\rightarrow L^2(\Omega)'$ be the corresponding linear operator generated by currying. That is, for each $u\in L^2(\Omega)$, the linear functional $\mathcal{A}u:L^2(\Omega)\rightarrow \mathbb{R}$ is 
%We approximate the operator $\mathcal{A}:L^2(\Omega)\rightarrow L^2(\Omega)'$ defined by
%\begin{equation*}
%	(\mathcal{A}u)(v) := a(v,u).
%\end{equation*}
%We seek to approximate operators $\mathcal{A}$ in the ``matrix free'' setting, in which access to $\mathcal{A}$ is available through application of $\mathcal{A}$ and $\mathcal{A}^T$ to arbitrary vectors, $u \mapsto\mathcal{A}u$ and $v \mapsto\mathcal{A}^Tv$. Here ($\mathcal{A}^Tv)(u) := (\mathcal{A}u)(v)$. 
%Integral kernel representation \eqref{eq:kernel_representation} is assumed to exist,
%e.g., by the Schwarz kernel theorem,
%but one cannot easily access entries $A(y,x)$ of the kernel. We assume that the impulse response of $\mathcal{A}$ is locally supported in the sense that the function 
%$y \mapsto A(y, x)$ is supported in a region near $y=x$, and we assume that $\mathcal{A}$ is locally translation invariant in the sense that
%\begin{equation*}
%A(y+h, x+h) \approx A(y,x),
%\end{equation*}
%so long as $h$ is not too large.
